Reasoning about a Capability Machine with Local Capabilities

### 2017-06-21 popl-2018/paper.tex
related, in progress

\dominique{Should we also discuss the fact that we only have a semantic model
  but not a logic?}

@@

Our logical relation is a unary, step-indexed Kripke logical relation
with recursive
worlds~\citep{Appel:2001:IMR:504709.504712,Ahmed2004semantics,Birkedal:2011:SKM:1926385.1926401},
closely related to the one used by \citet{Devriese:2016ObjCap} to formulate
capability safety in a high-level JavaScript-like lambda calculus. Our
Fundamental Theorem is similar to theirs and expresses
capability safety of the capability machine. Because we are not interested in
externally observable side-effects (like console output or memory access
traces), we do not require their notion of effect parametricity. Our logical
relation uses several ideas from previous work, like Kripke worlds with regions
containing state transition systems~\citep{Ahmed:popl09}, public/private future
worlds~\citep{Dreyer:jfp12} (see Section~\ref{sec:discussion} for a discussion), and
biorthogonality~\citep{pitts_operational_1998,benton_biorthogonality_2009-1,Hur:2011:KLR:1926385.1926402}.

>>>>

@@

Our logical relation is a unary, step-indexed Kripke logical relation
with recursive
worlds~\citep{Appel:2001:IMR:504709.504712,Ahmed2004semantics,Birkedal:2011:SKM:1926385.1926401},
closely related to the one used by \citet{Devriese:2016ObjCap} to formulate
capability safety in a high-level JavaScript-like lambda calculus. Our
Fundamental Theorem is similar to theirs and expresses
capability safety of the capability machine. Because we are not interested in
externally observable side-effects (like console output or memory access
traces), we do not require their notion of effect parametricity. Our logical
relation uses several ideas from previous work, like Kripke worlds with regions
containing state transition systems~\citep{Ahmed:popl09}, public/private future
worlds~\citep{Dreyer:jfp12} (see Section~\ref{sec:discussion} for a discussion), and
biorthogonality~\citep{pitts_operational_1998,benton_biorthogonality_2009-1,Hur:2011:KLR:1926385.1926402}.
Swasey et. al.\ have recently developed a \emph{logic}, OCPL,  for verification of
object capability patterns\citep{swasey:2017}. The logic is based on
Iris~\cite{iris,iris2,iris3}, a state of the art higher-order
concurrent separation logic and is formalized in Coq, building on the
Iris Proof Mode for Coq~\cite{ipm}.  
XXX HERE
